---
title: "TidyTemplate"
date: 2023-11-28
output: html_document
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(camcorder)
library(here)
library(glue)
library(ggtext)
library(showtext)
library(extrafont)
library(gganimate)
library(ggfx)
```

```{R}
tt_source <- "{datardis} package by Jonathan Kitt"
bg_color <- "black"
txt_color <- "#ffffff"
txt_color2 <- "gold"

yellow <- "#FFB702"  
blue <- "#1E9BD5"
green <- "#20C29D"
light_blue <- "#00E7EC"
red <- "#FF5674"

tt_family <- "montserrat"
tt_family_2 <-  "roboto"


font_add_google("Montserrat", tt_family)
font_add_google("Roboto", tt_family_2)

font_add("fa-brands",
         regular = here("Assets","Fonts","fontawesome-free-6.4.2-web","webfonts","fa-brands-400.ttf"))
font_add("fa-solid",
         regular = here("Assets","Fonts","fontawesome-free-6.4.2-web","webfonts","fa-solid-900.ttf"))
font_add("fa-regular",
         regular = here("Assets","Fonts","fontawesome-free-6.4.2-web","webfonts","fa-regular-400.ttf"))
showtext_auto(enable = T) 

X  <- str_glue("<span style='font-family:fa-brands'>&#xe61b;</span>")
GH <- str_glue("<span style='font-family:fa-brands'>&#xf09b;</span>")
MN <- str_glue("<span style='font-family:fa-brands'>&#xf4f6;</span>")
DT <- str_glue("<span style='font-family:fa-brands'>&#xf1c0;</span>")

tt_caption <- str_glue(
  "Steven Turnbull #TidyTuesday 2023-11-28<br>
  {X} @Turdbull {GH} @sturbull {MN} @turdbull<br>
  Data: {tt_source}
  "
)

tt_title_text    <- str_glue("Doctor Who Episodes")

tt_subtitle_text <- str_glue("Ratings across seasons from 2005 to the present day") 
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2023-11-28")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle, fig.width = 10, fig.height = 8}

df_episodes <-tt$drwho_episodes
df_episodes_clean <-  df_episodes %>%
  #just seasons
  filter(!is.na(season_number)) %>%
  #just episodes
  filter(type == "episode") %>%
  #tidy strings
  mutate(episode_number = str_pad(episode_number,
                                  width=2,side="left","0")) %>%
  mutate(season_number = str_pad(season_number,
                                 width=2,side="left","0")) %>%
  mutate(season_episode_char = as.character(paste0(season_number,".",episode_number))) %>%
  mutate(season_number = factor(as.factor(season_number),
                                levels= str_pad("1":"13",
                                width=2,side="left","0"))
         ) %>%
  mutate(season_episode_number = as.integer(as.factor(season_episode_char))) %>%
  arrange(season_episode_number) %>%
  #get number of episodes overall
  mutate(max_season_episode_number = max(season_episode_number)) %>%
  #record previous x and y values
  group_by(season_number) %>%
  mutate(x_lag = lag(episode_number), 
         y_lag = lag(rating),
  ) %>%
  ungroup() %>%
  #each point needs to represented in each frame 
  group_by(season_episode_number) %>%
  uncount(max_season_episode_number, .id = "frame") %>%
  # but only if the point has happpened already
  filter(season_episode_number<= frame) %>%
  ungroup() %>%
  mutate(row = row_number()) %>%
  #get the frame where each season starts and ends
  group_by(season_number) %>%
  mutate(season_start = min(frame),
         season_length = max(as.numeric(episode_number))) %>%
  ungroup() %>%
  #record where a point was active (i.e. the season is happening in the frame)
  group_by(season_episode_number) %>%
  mutate(
    active = between(frame,season_start,season_start+season_length),
    max_active_frame = max(frame[active]),
    # Make the line solid when active but reduce the alpha over time
    segment_alpha = case_when(active ~ 1,
                              !active ~pmax(0.1,(max_active_frame/frame)-0.6)
    ),
    point_alpha = case_when(active ~ 1,
                            !active ~ pmax(0.1,(max_active_frame/frame)-0.6)
                            
    )
    
  ) %>%
  ungroup() 

```
```{R}
#plotting data
tardis_blues_ordered <- c('#000e5b', '#002b81', '#003a93', '#1048a4', '#2f55b4', '#5571d4', '#677fe4', '#788ef5', '#8a9efe', '#9dafff', '#b0c1ff', '#c3d3ff', '#d5e4ff')

df_episodes_final <- df_episodes_clean %>% 
  mutate(episode_number = factor(episode_number,
                                 levels=str_pad("1":"13",
                                                width=2,
                                                side="left",
                                                "0"))
         ) %>%
  #make sure episode values are present across seasons for the x axis
  group_by(frame) %>%
  complete(episode_number)
```




# Visualize

Using your processed dataset, create your unique visualization.
```{R}
camcorder::gg_record(dir = here("outputs","2023-11-28"),
                     device = "png",
                     width = 8, height = 8,
                     units = "in", dpi = 320
)
```

```{r Visualize}

for(i in 1:max(df_episodes_final$frame)){
  frame_plot <- df_episodes_final %>% 
    filter(frame == i) %>%
    ggplot(aes(x = episode_number, y= rating,
               group = season_number)) +
    
    ggfx::with_outer_glow(
      geom_segment(aes(xend = x_lag, yend= y_lag,
                       alpha = segment_alpha,
                       group = season_number,
                       colour=season_number
      ),size=2
      ),
      colour = "white", sigma = 10,expand=3
    ) +
    ggfx::with_outer_glow(
      geom_text(data= df_episodes_final %>% 
                  filter(frame == i) %>%
                  arrange(desc(season_number)) %>%
                  head(1),
                x = "07", size=15, y=93,
                   aes(label = paste0("Season ", season_number),
                       colour=season_number)
                   
      ),
      colour = "white", sigma = 10,expand=1
    ) +
    scale_y_continuous(limits = c(75,95)) +
  scale_colour_manual(values=tardis_blues_ordered) +
    theme_classic(base_size = 20)+
    labs(
      title = tt_title_text,
      subtitle = tt_subtitle_text,
      caption = tt_caption,
      x = "Episode",y= "Rating") +
    scale_alpha_identity() +
    # transition_manual(frame) +
    # ease_aes('linear') +
    
    theme(
      plot.background = element_rect(colour=bg_color,fill = bg_color),
      panel.background = element_rect(colour=bg_color,fill = bg_color),
      plot.title.position = "plot",
      
      plot.title = element_textbox_simple(
        halign = 0.0,
        tt_family_2,
        #lineheight = 0.01,
        color = txt_color,
        face = "bold",
        size = 140,
        margin = margin(t = 2, r = 0, b = 0, l = 0)
      ),
      
      axis.text = element_text(size=40,colour = txt_color),
      
      axis.title = element_text(size=50,colour = txt_color),
      
      
      plot.subtitle = element_textbox_simple(
        halign = 0.0,
        #lineheight = 0.01,
        tt_family,
        color = txt_color2,
        #face = "bold",
        size = 50,
        margin = margin(t = 5, r = 0, b = 5, l = 0)
      ),
      
      plot.caption = element_textbox_simple(
        linewidth = 0.4, 
        family = tt_family, 
        color = txt_color,
        size = 30,
        lineheight = 0.1,
        margin = margin(t = 1, r = 0, b = 2, l = 2)
      ),
      plot.caption.position = "plot",
      
      legend.position = "none"
      
    )
  print(frame_plot)
}
```

```{R}
camcorder::gg_playback(name = here("outputs","Doctor_Who_2023_11_28.gif"),
                       image_resize = 800
                       )
```


